---
title: "course_8"
author: "abhinav palaparthy"
date: "4 November 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading the data 
```{r}
library(caret)
library(randomForest)
traindata <- read.csv("./training.csv")
testdata<-read.csv("./testing.csv")
```
## Data Exploration
Used str(traindata) in order to examine types of coloumns and dimensions. Used table(training$classe) to examine number of unique classe.We observe that all non numerical variables exempt classe are irrelevent in our model.Moreover there exists incomplete data sets which will make our analysis difficult , I have remove them altogether.
(not shown results to optimize space)
## Cleaning Data and preparation
```{r}
valid_traincols<-colSums(is.na(traindata))
valid_testcols<-colSums(is.na(testdata))
traindata<-traindata[,valid_traincols==0]
testdata<-testdata[,valid_traincols==0]

idw <- which(names(traindata) %in% c("X","raw_timestamp_part_1","raw_timestamp_part_2","cvtd_timestamp" ) )
traindata <- traindata[,-idw]
testdata<-testdata[,-idw]


classe <- traindata$classe
train<-traindata[,sapply(traindata,is.numeric)]
train$classe<-classe
test <- testdata[, sapply(testdata, is.numeric)]

```
## Creating cross validation set 
Now we split the preprocessed training data into training set and validation set.(70,30 split)
```{r}
set.seed(696569)
x <- createDataPartition(train$classe, p=0.70, list=F)
tset <- train[x, ]
vset <- train[-x, ]
```

## prediction 

```{r}
tr <- trainControl(method="cv", 5)
model_rf <- train(classe ~ ., data=tset, method="rf", trControl=tr, ntree = 250)
model_rf
```
use confusion matrix to measure sample error and accuracy 
```{r}
p <- predict(model_rf, vset)
confusionMatrix(vset$classe,p)
```
```{r}
accuracy <- postResample(p,vset$classe)
accuracy
```
## applying model to test dataset 
```{r}
outcome<-predict(model_rf,test[, -length(names(test))])
outcome
```
